Favourable Conservation Status (FCS): <br> Analysis of Bauer et al. (unpublished) Field experiment

### 2022-11-11 R/model_fcs_markdown.Rmd
Update Markdown

```{r echo = FALSE}
rm(list = ls())
rm(list = setdiff(ls(), c(
  "m_simple", "m_full", "m1", "m3", "m3_flat", "m_simple_flat", "m3_iter"
  )))
```

@@

```{r}
prior_summary(m_1)
bayes_R2(m_1, probs = c(0.05, 0.5, 0.95),
         re_formula =  ~ (1 | site/plot) + (1 | botanist_year)) 
bayes_R2(m_2, probs = c(0.05, 0.5, 0.95),
         re_formula =  ~ (1 | site/plot) + (1 | botanist_year)) 
bayes_R2(m_1, probs = c(0.05, 0.5, 0.95),
         re_formula = 1 ~ 1)
bayes_R2(m_2, probs = c(0.05, 0.5, 0.95),
         re_formula = 1 ~ 1)
draws1
mcmc_intervals(
  posterior1,
  prob = 0.5,
  prob_outer = 0.95,
  point_est = "mean"
)
sjPlot::plot_model(m_1, m_2, type = "est")
sjPlot::plot_model(m_2, type = "est")
sjPlot::plot_model(
  m_1, m_2, type = "est", ppd = TRUE,
  terms = c(
    "sand_ratio", "substrate_depth", "target_type",
    "seed_density",  "exposition", "survey_year_fct"
    )
  )
```

@@

```{r}
(emm <- emmeans(m_1, revpairwise ~ target_type + sand_ratio |
                  exposition | survey_year_fct, type = "response"))
(emm <- emmeans(m_1, revpairwise ~ substrate_depth + sand_ratio |
                  exposition | survey_year_fct, type = "response"))
(emm <- emmeans(m_1, revpairwise ~ seed_density |
                  exposition | survey_year_fct, type = "response"))
```

>>>>

```{r echo = FALSE}
rm(list = ls())
```

@@

```{r}
prior_summary(m_2, all = FALSE)
bayes_R2(m_1, probs = c(0.05, 0.5, 0.95),
         re_formula =  ~ (1 | site/plot) + (1 | botanist_year)) 
bayes_R2(m_2, probs = c(0.05, 0.5, 0.95),
         re_formula =  ~ (1 | site/plot) + (1 | botanist_year)) 
bayes_R2(m_1, probs = c(0.05, 0.5, 0.95),
         re_formula = 1 ~ 1)
bayes_R2(m_2, probs = c(0.05, 0.5, 0.95),
         re_formula = 1 ~ 1)
draws2
mcmc_intervals(
  posterior1,
  prob = 0.66,
  prob_outer = 0.95,
  point_est = "mean"
)
mcmc_intervals(
  posterior2,
  prob = 0.5,
  prob_outer = 0.95,
  point_est = "mean"
)
```

@@

```{r}
(emm <- emmeans(m_1, revpairwise ~ target_type + sand_ratio |
                  exposition | survey_year_fct, type = "response"))
```
